Estimating the Financial Impact of Wildfire Smoke on US National parks

### 2020-05-21 Markdown Documents/Manuscript.Rmd
small plot chages

```{r echo=FALSE, cache=TRUE, message=FALSE,warning=FALSE, fig.height = 9, fig.width = 12}
pars+ggplot2::ggtitle("Posterior medians with 50% and 90% intervals")+
  ggplot2::scale_y_discrete(name ="Park",labels=rev(PNames),limits=rev(limits))+
  mytheme+scale_x_continuous(name="Parameter Value", labels = scales::comma)
```

@@

```{r echo=FALSE, warning=FALSE, cache=TRUE,message=FALSE, fig.height = 6, fig.width = 12}
library(scales)
p1<-dat%>%filter(UnitCode == "GLAC")%>%
    ggplot(.,aes(x=date))+
    geom_ribbon(aes(ymin=PredNoSmoke5CI, ymax=PredNoSmoke95CI),fill="#1f78b4",alpha=0.2)+
    geom_ribbon(aes(ymin=PredNoSmoke25CI, ymax=PredNoSmoke75CI),fill="#1f78b4",alpha=0.5)+
    geom_line(aes(y=RecreationVisits,color="grey"),size=1.25)+
    geom_point(aes(y=RecreationVisits,color="black"),size=2)+
    geom_line(aes(y=PredNoSmoke50CI,color="#1f78b4"),linetype="longdash",size=1.25)+theme_classic()+
    mytheme + scale_y_continuous(name="Recreational Visits", labels = scales::comma)+
    scale_x_continuous(name="Date",breaks=c(1980,1990,2000,2010,2018))+
    scale_color_identity(name = "",
                         breaks = c("black", "#1f78b4"),
                         labels = c("Observed", "Median Estimate Minimum Smoke"),
                         guide = "legend")+ggtitle("Glacier National Park")+theme(legend.position="top")+
    theme(axis.title.x=element_blank(),
          axis.text.x=element_blank(),
          axis.ticks.x=element_blank(),
          axis.line.x = element_blank())

@@

```{r echo=FALSE, warning=FALSE, cache=TRUE,message=FALSE, fig.height = 6, fig.width = 12}
library(scales)
p1<-dat%>%filter(UnitCode == "OLYM")%>%
    ggplot(.,aes(x=date))+
    geom_ribbon(aes(ymin=PredNoSmoke5CI, ymax=PredNoSmoke95CI),fill="#1f78b4",alpha=0.2)+
    geom_ribbon(aes(ymin=PredNoSmoke25CI, ymax=PredNoSmoke75CI),fill="#1f78b4",alpha=0.5)+
    geom_line(aes(y=RecreationVisits,color="grey"),size=1.25)+
    geom_point(aes(y=RecreationVisits,color="black"),size=2)+
    geom_line(aes(y=PredNoSmoke50CI,color="#1f78b4"),linetype="longdash",size=1.25)+theme_classic()+
    mytheme + scale_y_continuous(name="Recreational Visits", labels = scales::comma)+
    scale_x_continuous(name="Date",breaks=c(1980,1990,2000,2010,2018))+
    scale_color_identity(name = "",
                         breaks = c("black", "#1f78b4"),
                         labels = c("Observed", "Median Estimate Minimum Smoke"),
                         guide = "legend")+ggtitle("Olympic National Park")+theme(legend.position="top")+
    theme(axis.title.x=element_blank(),
          axis.text.x=element_blank(),
          axis.ticks.x=element_blank(),
          axis.line.x = element_blank())

>>>>

```{r echo=FALSE, cache=TRUE, message=FALSE,warning=FALSE, fig.height = 9, fig.width = 12}
pars+ggplot2::ggtitle("Posterior medians with 50% and 90% intervals")+
  ggplot2::scale_y_discrete(name ="Park",labels=rev(PNames),limits=rev(limits))+
  mytheme+scale_x_continuous(name="Parameter Value", labels = scales::comma)+
  theme(panel.grid.major.y = element_line(color = "lightgrey", linetype="dotted")) 
```

@@

```{r echo=FALSE, warning=FALSE, cache=TRUE,message=FALSE, fig.height = 6, fig.width = 12}
library(scales)
p1<-dat%>%filter(UnitCode == "GLAC")%>%
    ggplot(.,aes(x=date))+
    geom_ribbon(aes(ymin=PredNoSmoke5CI, ymax=PredNoSmoke95CI),fill="#1f78b4",alpha=0.2)+
    geom_ribbon(aes(ymin=PredNoSmoke25CI, ymax=PredNoSmoke75CI),fill="#1f78b4",alpha=0.5)+
    geom_line(aes(y=RecreationVisits,color="darkgrey"),size=1.25)+
    geom_point(aes(y=RecreationVisits,color="black"),size=2)+
    geom_line(aes(y=PredNoSmoke50CI,color="#1f78b4"),linetype="longdash",size=1.25)+theme_classic()+
    mytheme + scale_y_continuous(name="Recreational Visits", labels = scales::comma)+
    scale_x_continuous(name="Date",breaks=c(1980,1990,2000,2010,2018))+
    scale_color_identity(name = "",
                         breaks = c("black", "#1f78b4"),
                         labels = c("Observed", "Median Estimate Minimum Smoke"),
                         guide = "legend")+ggtitle("Glacier National Park")+theme(legend.position="top")+
    theme(axis.title.x=element_blank(),
          axis.text.x=element_blank(),
          axis.ticks.x=element_blank(),
          axis.line.x = element_blank())

@@

```{r echo=FALSE, warning=FALSE, cache=TRUE,message=FALSE, fig.height = 6, fig.width = 12}
library(scales)
p1<-dat%>%filter(UnitCode == "OLYM")%>%
    ggplot(.,aes(x=date))+
    geom_ribbon(aes(ymin=PredNoSmoke5CI, ymax=PredNoSmoke95CI),fill="#1f78b4",alpha=0.2)+
    geom_ribbon(aes(ymin=PredNoSmoke25CI, ymax=PredNoSmoke75CI),fill="#1f78b4",alpha=0.5)+
    geom_line(aes(y=RecreationVisits,color="darkgrey"),size=1.25)+
    geom_point(aes(y=RecreationVisits,color="black"),size=2)+
    geom_line(aes(y=PredNoSmoke50CI,color="#1f78b4"),linetype="longdash",size=1.25)+theme_classic()+
    mytheme + scale_y_continuous(name="Recreational Visits", labels = scales::comma)+
    scale_x_continuous(name="Date",breaks=c(1980,1990,2000,2010,2018))+
    scale_color_identity(name = "",
                         breaks = c("darkgrey", "#1f78b4"),
                         labels = c("Observed", "Median Estimate Minimum Smoke"),
                         guide = "legend")+ggtitle("Olympic National Park")+theme(legend.position="top")+
    theme(axis.title.x=element_blank(),
          axis.text.x=element_blank(),
          axis.ticks.x=element_blank(),
          axis.line.x = element_blank())
